Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-07 article/article.Rmd
Commit 2024-06-07 19:12

On multiple sites, cloud enhancements (CE) have been reported to be able to briefly
exceed the value of the solar constant, resulting of clearness indices above unit. A
summary of extreme enchantment cases (ECE) has been compiled by @Martins2022. There
are also; some practical implications of the cloud enchantments.  The intensity and
duration of enhancements can effect the efficiency and stability of photovoltaic
power production [@Lappalainen2020; @Jaervelae2020]; while ECEs have the potential to
compromise the integrity of photovoltaic plants infrastructure [@DoNascimento2019].
It has also been demonstrated, that these events can interfere in the comparison of
ground-based and satellite observations [@Damiani2018]

>>>>

On multiple sites, cloud enhancements (CE) have been reported to be able to briefly
exceed the value of the solar constant, resulting of clearness indices above unit. A
summary of extreme enchantment cases (ECE) has been compiled by @Martins2022. There
are also; some practical implications of the cloud enchantments.  The intensity and
duration of enhancements can effect the efficiency and stability of photovoltaic
power production [@Lappalainen2020; @Jaervelae2020]; while ECEs have the potential to
compromise the integrity of photovoltaic plants infrastructure [@DoNascimento2019].
It has also been demonstrated that these events can interfere in the comparison of
ground-based and satellite observations [@Damiani2018].  Global warming has likely
affected cloud coverage in the last few decades. @Liu2023 reported increases in cloud
cover over the tropical and subtropical oceans and decreases over most continents,
while @Dong2022 reported decreases over North America and Europe. To our knowledge,
there is no evidence on whether this trend has affected also the number and strength
of CE events.

### 2024-06-07 article/article.tex
Commit 2024-06-07 19:12

On multiple sites, cloud enhancements (CE) have been reported to be able
to briefly exceed the value of the solar constant, resulting of
clearness indices above unit. A summary of extreme enchantment cases
(ECE) has been compiled by \citet{Martins2022}. There are also; some
practical implications of the cloud enchantments. The intensity and
duration of enhancements can effect the efficiency and stability of
photovoltaic power production \citep{Lappalainen2020, Jaervelae2020};
while ECEs have the potential to compromise the integrity of
photovoltaic plants infrastructure \citep{DoNascimento2019}. It has also
been demonstrated, that these events can interfere in the comparison of
ground-based and satellite observations \citep{Damiani2018}

>>>>

On multiple sites, cloud enhancements (CE) have been reported to be able
to briefly exceed the value of the solar constant, resulting of
clearness indices above unit. A summary of extreme enchantment cases
(ECE) has been compiled by \citet{Martins2022}. There are also; some
practical implications of the cloud enchantments. The intensity and
duration of enhancements can effect the efficiency and stability of
photovoltaic power production \citep{Lappalainen2020, Jaervelae2020};
while ECEs have the potential to compromise the integrity of
photovoltaic plants infrastructure \citep{DoNascimento2019}. It has also
been demonstrated that these events can interfere in the comparison of
ground-based and satellite observations \citep{Damiani2018}. Global
warming has likely affected cloud coverage in the last few decades.
\citet{Liu2023} reported increases in cloud cover over the tropical and
subtropical oceans and decreases over most continents, while
\citet{Dong2022} reported decreases over North America and Europe. To
our knowledge, there is no evidence on whether this trend has affected
also the number and strength of CE events.
